Automatic conversion of colloquial Finnish to standard Finnish

### 2015-01-26 finnormal-nodalida-2015/finnormal2015.tex
more fixes
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58606 72bbbca6-d526-0410-a7d9-f06f51895060

\begin{table*}
  \centering
  \begin{tabular}{|l|l|r|l|}
    \hline
    \textbf{Input:} & \multicolumn{3}{l|}{M\"{a} oon Tomminkaa `I am with Tommi'.} \\
    \hline
    \multirow{2}{*}{Step 1}  & M\"{a} oon Tomminkaa & & apply rule 1: \\
                             & Min\"{a} oon Tomminkaa & & m\"{a} $\rightarrow$ min\"{a} \\
    \hline
    \multirow{2}{*}{Step 2}  & M\"{a} oon Tomminkaa & & apply rule 2: \\
                             & Min\"{a} oon Tomminkaa & & oon $\rightarrow$ olen \\
                             & M\"{a} olen Tomminkaa & & \\
                             & Min\"{a} olen Tomminkaa & & \\
    \hline
    \multirow{2}{*}{Step 3}  & M\"{a} oon Tomminkaa   & & apply rule 3:\\
                             & Min\"{a} oon Tomminkaa &  & (?+)nkaa $\rightarrow$ \textbackslash1n kanssa \\
                             & M\"{a} olen Tomminkaa  & &\\
                             & Min\"{a} olen Tomminkaa  & &\\
                             & M\"{a} oon Tommin kanssa  & &\\
                             & Min\"{a} oon Tommin kanssa  & &\\
                             & M\"{a} olen Tommin kanssa  & &\\
                             & Min\"{a} olen Tommin kanssa  & &\\
    \hline
    \multirow{2}{*}{Step 4} &  Min\"{a} olen Tommin kanssa & -4.5811 & rank candidates \\
                            &  Min\"{a} oon Tommin kanssa & -7.8174 & \\
                            &  M\"{a} olen Tommin kanssa & -8.0941 & \\
                            &  M\"{a} oon Tommin kanssa & -8.8651 & \\
                            &  Min\"{a} olen Tomminkaa & -9.2045 & \\
                            &  Min\"{a} oon Tomminkaa & -12.4408 & \\
                            &  M\"{a} olen Tomminkaa & -12.7176 & \\
                            &  M\"{a} oon Tomminkaa & -13.4885 & \\

@@

The target-language model corpus used was the same as in the unsupervised experiments.

>>>>

\begin{table*}
  \centering
  \begin{tabular}{|l|l|r|l|}
    \hline
    \textbf{Input:} & \multicolumn{3}{l|}{M\"{a} oon Tomminkaa `I am with Tommi'.} \\
    \hline
    \multirow{2}{*}{Step 1}  & M\"{a} oon Tomminkaa & & apply rule 1: \\
                             & Min\"{a} oon Tomminkaa & & ~~~m\"{a} $\rightarrow$ min\"{a} \\
    \hline
    \multirow{2}{*}{Step 2}  & M\"{a} oon Tomminkaa & & apply rule 2: \\
                             & Min\"{a} oon Tomminkaa & & ~~~oon $\rightarrow$ olen \\
                             & M\"{a} olen Tomminkaa & & \\
                             & Min\"{a} olen Tomminkaa & & \\
    \hline
    \multirow{2}{*}{Step 3}  & M\"{a} oon Tomminkaa   & & apply rule 3:\\
                             & Min\"{a} oon Tomminkaa &  & ~~~(?+)nkaa $\rightarrow$ \textbackslash1n kanssa \\
                             & M\"{a} olen Tomminkaa  & &\\
                             & Min\"{a} olen Tomminkaa  & &\\
                             & M\"{a} oon Tommin kanssa  & &\\
                             & Min\"{a} oon Tommin kanssa  & &\\
                             & M\"{a} olen Tommin kanssa  & &\\
                             & Min\"{a} olen Tommin kanssa  & &\\
    \hline
    \multirow{2}{*}{Step 4} &  Min\"{a} olen Tommin kanssa & -4.5811 & rank candidates \\
                            &  Min\"{a} oon Tommin kanssa & -7.8174 & \\
                            &  M\"{a} olen Tommin kanssa & -8.0941 & \\
                            &  M\"{a} oon Tommin kanssa & -8.8651 & \\
                            &  Min\"{a} olen Tomminkaa & -9.2045 & \\
                            &  Min\"{a} oon Tomminkaa & -12.4408 & \\
                            &  M\"{a} olen Tomminkaa & -12.7176 & \\
                            &  M\"{a} oon Tomminkaa & -13.4885 & \\

@@

The target-language model corpus, trained using KenLM \cite{heafield2011}, used was the same as in the unsupervised experiments.
